---
title: "hw6"
author: "Hao Sun"
date: "11/19/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("tidyverse")
library(modelr)
library(mgcv)
```

## Problem 1

In this problem, you will analyze data gathered to understand the effects of several variables on a child’s birthweight. This dataset, available here, consists of roughly 4000 children and includes the following variables:

babysex: baby’s sex (male = 1, female = 2)
bhead: baby’s head circumference at birth (centimeters)
blength: baby’s length at birth (centimeteres)
bwt: baby’s birth weight (grams)
delwt: mother’s weight at delivery (pounds)
fincome: family monthly income (in hundreds, rounded)
frace: father’s race (1 = White, 2 = Black, 3 = Asian, 4 = Puerto Rican, 8 = Other, 9 = Unknown)
gaweeks: gestational age in weeks
malform: presence of malformations that could affect weight (0 = absent, 1 = present)
menarche: mother’s age at menarche (years)
mheigth: mother’s height (inches)
momage: mother’s age at delivery (years)
mrace: mother’s race (1 = White, 2 = Black, 3 = Asian, 4 = Puerto Rican, 8 = Other)
parity: number of live births prior to this pregnancy
pnumlbw: previous number of low birth weight babies
pnumgsa: number of prior small for gestational age babies
ppbmi: mother’s pre-pregnancy BMI
ppwt: mother’s pre-pregnancy weight (pounds)
smoken: average number of cigarettes smoked per day during pregnancy
wtgain: mother’s weight gain during pregnancy (pounds)


Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).

```{r}
birthweight = read_csv("./data/birthweight.csv")%>%janitor::clean_names()

race_fctr_lv = c("White", "Black", "Asian", "Puerto Rican", "Other", "Unknown")



birthweight = read_csv("./data/birthweight.csv")%>%janitor::clean_names()%>%
  ###Recode the factors
  mutate(bwt =bwt , 
    babysex = recode_factor(babysex, `1` = "male" , `2` = "female"),
         malform = recode_factor(malform, `1` = "present" , `0` = "absent"),
                frace = forcats::fct_reorder(factor(race_fctr_lv[frace]),frace),
               mrace = forcats::fct_reorder(factor(race_fctr_lv[mrace]),mrace))%>%select(bwt,babysex,mrace,frace,malform,bhead,blength:wtgain)%>%mutate(id=seq(1,4342))


###Have a look on the relationships of birthweight to other variable.
birthweight_vis_1 = birthweight%>% pivot_longer(names_to = "para", values_to = "value" , cols =  bhead:fincome  )
birthweight_vis_2 = birthweight%>% pivot_longer(names_to = "para", values_to = "value" , cols =  gaweeks:momage  )
birthweight_vis_3 = birthweight%>% pivot_longer(names_to = "para", values_to = "value" , cols =  parity:ppbmi  )
birthweight_vis_4 = birthweight%>% pivot_longer(names_to = "para", values_to = "value" , cols =  ppwt:id  )


birthweight_vis_1%>%ggplot(aes(x=bwt,y = value))+geom_smooth()+geom_point(alpha = 0.2)+facet_grid(rows = "para",scales = "free",space = "fix")
birthweight_vis_2%>%ggplot(aes(x=bwt,y = value))+geom_smooth()+geom_point(alpha = 0.2)+facet_grid(rows = "para",scales = "free",space = "fix")
birthweight_vis_3%>%ggplot(aes(x=bwt,y = value))+geom_smooth()+geom_point(alpha = 0.2)+facet_grid(rows = "para",scales = "free",space = "fix")
birthweight_vis_4%>%ggplot(aes(x=bwt,y = value))+geom_smooth()+geom_point(alpha = 0.2)+facet_grid(rows = "para",scales = "free",space = "fix")



```



Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

__Answer__ 
By looking at the scatterpoint graph of birthweight vs other indicators, a selection of indicators was chosen. Besides, family income was included as there is research suggesting family income is correlated with birthweight

```{r}
colnames(birthweight)

reg_bwt <- lm(bwt~blength+fincome+gaweeks+wtgain+bhead*babysex+mrace+frace,data = birthweight)

reg_bwt%>%summary()

birthweight_rp <-birthweight%>%modelr::add_residuals(reg_bwt)%>%modelr::add_predictions(reg_bwt)

birthweight_rp%>%ggplot(aes(x=pred,y=resid))+geom_point()

```



Compare your model to two others:

One using length at birth and gestational age as predictors (main effects only)
```{r}

model_ref1<-birthweight%>%lm(bwt~gaweeks+blength ,data = .)
model_ref1%>%summary()
```

One using head circumference, length, sex, and all interactions (including the three-way interaction) between these
```{r}
model_ref2<-birthweight%>%lm(bwt~blength+bhead+babysex+blength*bhead+babysex*blength+bhead*babysex+blength*bhead*babysex,data = .)
model_ref2%>%summary()
```

Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.
```{r}
cv_df = 
  crossv_mc(birthweight, 100)

cv_df = 
  cv_df %>% 
  mutate(reg_bwt  = map(train, ~lm(bwt~blength+fincome+gaweeks+wtgain+bhead*babysex+mrace+frace,data = .)),
         model_ref1  = map(train, ~lm(bwt~gaweeks+blength ,data = .)),
         model_ref2  = map(train, ~lm(bwt~blength+bhead+babysex+blength*bhead+babysex*blength+bhead*babysex+blength*bhead*babysex,data = .)))%>% 
  mutate(rmse_reg_bwt = map2_dbl(reg_bwt, test, ~rmse(model = .x, data = .y)),
         rmse_model_ref1 = map2_dbl(model_ref1, test, ~rmse(model = .x, data = .y)),
         rmse_model_ref2 = map2_dbl(model_ref2, test, ~rmse(model = .x, data = .y)))


cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

Note that although we expect your model to be reasonable, model building itself is not a main idea of the course and we don’t necessarily expect your model to be “optimal”.
__Answer__
As it occured, the model construsted by me outperform the two given model as it have less cross-validated prediction error 


### Problem 2

For this problem, we’ll use the 2017 Central Park weather data that we’ve seen elsewhere. The code chunk below (adapted from the course website) will download these data.

```{r}

weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

```



The boostrap is helpful when you’d like to perform inference for a parameter / value / summary that doesn’t have an easy-to-write-down distribution in the usual repeated sampling framework. We’ll focus on a simple linear regression with tmax as the response and tmin as the predictor, and are interested in the distribution of two quantities estimated from these data:

r̂2 log(β̂0∗β̂1)

Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of these two quantities. Plot the distribution of your estimates, and describe these in words. 

```{r}

boot_straps = 
  weather_df %>% 
  modelr::bootstrap(n = 5000)

logbeta = function(df){log(df[[1,2]]*df[[2,2]])}
rsquare = function(df){pull(df,"r.squared")}

bs_result = boot_straps%>%
mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ))

bs_result=bs_result %>%mutate(
    result =  map(models, broom::tidy),
    results_logbeta = map_dbl(result, logbeta),
   results_r2 = map(models, broom::glance),
    results_r2 = map_dbl(results_r2,.%>%pull(r.squared)))
    
  

bs_result=bs_result%>%select(-strap,-models,-result)
bs_result%>%pivot_longer(names_to = "para", values_to = "value", cols = results_logbeta:results_r2)%>%
  ggplot()+geom_density(aes(x = value ,color = para) )+facet_grid(~para,scales = "free")


```


Using the 5000 bootstrap estimates, identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for
r̂2 and log(β̂0∗β̂1)


__Answer__
The 95% confidence interval for log(β̂0∗β̂1) is as followed
 
```{r}
pull(bs_result,results_logbeta)%>%quantile( probs = c(2.5,97.5)/100)
```
 The 95% confidence interval for r̂^2 is as followed
```{r}
pull(bs_result,results_r2)%>%quantile( probs = c(2.5,97.5)/100)
```



